---
title: "Final Project"
output: github_document
author: "Adrian Ortiz, Juan Ramirez JR"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment="")
library(tidyverse)
library(lubridate)
library(scales)
library(readr)
#include other packages needed here
```

```{r, eval=FALSE, include=FALSE}
#include data cleaning code here, with comments on what each step is doing the indicators above eval=FALSE and include=FALSE will stop the code from running again when you knit the document while still keeping the code in the document
#use write_csv() to write your tidy data into a new csv file
```

```{r}
#use read_csv() to import your new tidy data include any variable specifications here as needed
driver_standings <- read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-09-07/driver_standings.csv")
qualifying_times <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-09-07/qualifying.csv")
constructor_standings <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-09-07/constructor_standings.csv")
constructors <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-09-07/constructors.csv")
```

## Introduction
Description of data and problem(s) you are solving.  Include data source(s) here, either through citation or link to webpage.
>Question 1: Of the fastest drivers in Qualifying Round #3, who has the most wins in Abu Dhabi?
>Question 2: Which team had the most wins in the 2021 season?

## Graphic 1
Provide a brief description of your goal with your created graphic and what it demonstrates
```{r}
#include code for any data manipulation and variable creation used to create the graphic as well as the code for the graph creation - be sure to comment all code with description of steps being completed with each line of code
qualifying_times %>% 
  mutate(q3 = replace(q3, q3 == "\\N", "0.0")) %>% 
  filter(raceId == "17") %>% 
  select(driverId, q3) %>% 
  filter(q3 != "0.0") %>% 
  arrange(q3) %>% 
  write_csv("clean_times.csv")
```

```{r}
driver_standings %>% 
  filter(raceId == "17") %>% 
  mutate(label = driverId) %>% 
  write_csv("clean_drivers.csv") %>% 
  
  top_n(3, wins) %>%
  ggplot(aes(x = driverId, y = wins)) +
  geom_col(aes(fill = wins, x = reorder(driverId, wins), y = wins), show.legend = FALSE) +
  labs(title = "Fastest Q3 Drivers' wins in Abhu Dhabi GP (any year)")
```
> The fastest driver from Q3 with the most wins in Abu Dhabi is driverId #18, which is Jenson Button.

## Graphic 2 - Which team has the most all-time wins?
Provide a brief description of your goal with your created graphic and what it demonstrates

For this graphic, we wanted to see which F1 team currently has the most wins all-time. In order to do this, we needed to look at the provided "constructor_standings" data set to determine who has the most wins.  
We did notice that there are some teams without wins, so we had to remove those first before we could sort the data in order.  
The end result is a nice depiction of the top three teams in F1 to-date: The top team is Mercedes, followed by Ferrari, and finally McLaren.
```{r}
#include code for any data manipulation and variable creation used to create the graphic as well as the code for the graph creation - be sure to comment all code with description of steps being completed with each line of code
constructor_standings %>%
  filter(wins != 0) %>% 
  arrange(desc(wins)) %>% 
  write_csv("clean_constructor_standings.csv") %>% 

  top_n(10, wins) %>% 
  ggplot(aes(x = constructorId, y = wins)) +
    geom_col(aes(fill = wins, x = reorder(constructorId, wins), y = wins), show.legend = FALSE) +
    labs(title = "Teams with the most wins (Total)") + 
    theme_classic()

```
