---
title: "Final Project"
output: github_document
author: "Adrian Ortiz, Juan Ramirez JR"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment="")
library(tidyverse)
library(lubridate)
library(scales)
library(readr)
#include other packages needed here
```

```{r, eval=FALSE, include=FALSE}
#include data cleaning code here, with comments on what each step is doing the indicators above eval=FALSE and include=FALSE will stop the code from running again when you knit the document while still keeping the code in the document
#use write_csv() to write your tidy data into a new csv file
```

```{r}
#use read_csv() to import your new tidy data include any variable specifications here as needed
driver_standings <- read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-09-07/driver_standings.csv")
qualifying_times <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-09-07/qualifying.csv")
constructor_standings <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-09-07/constructor_standings.csv")
constructors <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-09-07/constructors.csv")
```

## Introduction
Description of data and problem(s) you are solving.  Include data source(s) here, either through citation or link to webpage.
>Question 1: Of the fastest drivers in Qualifying Round #3, who has the most wins in Abu Dhabi?
>Question 2: Which team had the most wins in the 2021 season?

## Graphic 1
Provide a brief description of your goal with your created graphic and what it demonstrates

For this problem, we are trying to find out which of the fastest drivers in Qualifying round #3 had the most wins in a specific course: Abu Dhabi. We chose Abu Dhabi because it is one of the more complex and iconic circuits in F1, not to mention the final circuit in most F1 seasons.  
We take some data from the Q3 times for each driver. We decided to skip Q1 and Q2 because we were ONLY interested in drivers who were fast enough to survive the first two rounds of qualifying and move on the the third and final round.  
We started by removing any values which were marked NULL which usually indicate some sort of mechanical failure or other issue that took a driver out of Q3. We then take a look at the number of total wins these drivers had.  

The end result is graphic for the fastest Q3 drivers compared by total wins.

```{r}
#include code for any data manipulation and variable creation used to create the graphic as well as the code for the graph creation - be sure to comment all code with description of steps being completed with each line of code
qualifying_times %>% 
  mutate(q3 = replace(q3, q3 == "\\N", "0.0")) %>% #replaces \\N with 0.0 in the qualifying time #3
  filter(raceId == "17") %>% #filters to just get raceId's 17
  select(driverId, q3) %>% #selects just the driverId and q3
  filter(q3 != "0.0") %>% #filters anything that doesn't have a time of 0.0 for q3
  arrange(q3) %>% #arranges the data
  write_csv("clean_times.csv") #writes a new csv file
```

```{r}
driver_standings %>% 
  filter(raceId == "17") %>% #filters anything with raceId = 17
  mutate(label = driverId) %>%  #makes a new column called label with driverId's
  write_csv("clean_drivers.csv") %>% #writes csv file
  
  top_n(3, wins) %>% #gets the top 3 of wins
  ggplot(aes(x = driverId, y = wins)) + #starts the ggplot
  geom_col(aes(fill = wins, x = reorder(driverId, wins), y = wins), show.legend = FALSE) + #creates the col graph
  labs(title = "Fastest Q3 Drivers' wins in Abhu Dhabi GP (any year)") #adds labels
```
> The fastest driver from Q3 with the most wins in Abu Dhabi is driverId #18, which is Jenson Button.

## Graphic 2 - Which team has the most all-time wins?
Provide a brief description of your goal with your created graphic and what it demonstrates

For this graphic, we wanted to see which F1 team currently has the most wins all-time. In order to do this, we needed to look at the provided "constructor_standings" data set to determine who has the most wins.  
We did notice that there are some teams without wins, so we had to remove those first before we could sort the data in order.  
The end result is a nice depiction of the top three teams in F1 to-date: The top team is Mercedes, followed by Ferrari, and finally McLaren.
```{r}
#include code for any data manipulation and variable creation used to create the graphic as well as the code for the graph creation - be sure to comment all code with description of steps being completed with each line of code
constructor_standings %>%
  filter(wins != 0) %>% 
  arrange(desc(wins)) %>% 
  write_csv("clean_constructor_standings.csv") %>% 

  top_n(10, wins) %>% 
  ggplot(aes(x = constructorId, y = wins)) +
    geom_col(aes(fill = wins, x = reorder(constructorId, wins), y = wins), show.legend = FALSE) +
    labs(title = "Teams with the most wins (Total)") + 
    theme_classic()

```
